MO443 - Assignment I

### 2019-09-12 main.tex
Updates from Overleaf

\begin{figure}[H]
	\centering
	\subfloat{
		{
			\includegraphics[scale=0.7]{figures/input/baboon}
		}
		\label{fig:baboon}
	}
	\quad
	\subfloat{
		{
			\includegraphics[scale=0.7]{figures/input/david}
		}
		\label{fig:david}
	}
	\quad
	\subfloat{
		{
			\includegraphics[scale=0.7]{figures/input/juquinha}
		}
		\label{fig:juquinha}
	}
	\quad
	\subfloat{
		{
			\includegraphics[scale=0.7]{figures/input/bee}
		}
		\label{fig:bee}
	}
	\quad
	\subfloat{
		{
			\includegraphics[scale=0.7]{figures/input/peppers}
		}
		\label{fig:peppers}
	}
	\quad
	\subfloat{
		{
			\includegraphics[scale=0.7]{figures/input/peppers}
		}
		\label{fig:peppers}
	}
	\caption{A sample of the images used in the experiments.}
	\label{fig:input}
\end{figure}

@@

In this experiment we performed a colored dithering and a grayscaled one. We also used Floyd and Steinberg's erro diffusion

\begin{figure}[H]
	\centering
	\subfloat{
		{
			\includegraphics[scale=0.7]{figures/left2right/flo_color_baboon}
		}
		\label{fig:baboon_color}
	}
	\quad
	\subfloat{
		{
			\includegraphics[scale=0.7]{figures/left2right/flo_gray_baboon}
		}
		\label{fig:baboon_gray}
	}
	\caption{Traversal directions experimented on.}
	\label{fig:baboon_colorspace}
\end{figure}

@@

@@

>>>>

\begin{figure}[H]
\centering
\subfloat{
	{
		\includegraphics[scale=0.7]{figures/input/bee}
	}
	\label{fig:peppers}
}
\subfloat{
	{
		\includegraphics[scale=0.7]{figures/input/bee}
	}
	\label{fig:peppers}
}
\quad
\subfloat{
	{
		\includegraphics[scale=0.7]{figures/input/bee}
	}
	\label{fig:peppers}
}
\subfloat{
	{
		\includegraphics[scale=0.7]{figures/input/bee}
	}
	\label{fig:peppers}
}
\quad
\subfloat{
	{
		\includegraphics[scale=0.7]{figures/input/bee}
	}
	\label{fig:peppers}
}
\subfloat{
	{
		\includegraphics[scale=0.7]{figures/input/bee}
	}
	\label{fig:peppers}
}
\caption{A sample of the images used in the experiments.}
\label{fig:input}
\end{figure}

@@

In this experiment we performed a colored dithering and a grayscaled one. Although we are not exploring the effects of error diffusion and traversal direction, we also used Floyd and Steinberg's erro diffusion and traversed the image from left to right, top to bottom. Figure~\ref{fig:baboon_colorspace} shows the resulting dithering, in it we can observe that overall features of the image are kept, it is still possible to identify the baboon in frame, as it is the intention of dithering. But on a closer inspection it is also possible to notice a drop in quality of both images, also an expected effect, for instance the lower lip of the baboon has been filled with noise and mixes with the fur.

\begin{figure}[H]
	\centering
	\subfloat{
		{
			\includegraphics[scale=0.7]{figures/left2right/flo_color_baboon}
		}
		\label{fig:baboon_color}
	}
	\quad
	\subfloat{
		{
			\includegraphics[scale=0.7]{figures/left2right/flo_gray_baboon}
		}
		\label{fig:baboon_gray}
	}
	\caption{Color and Grayscale dithering on Baboon.}
	\label{fig:baboon_colorspace}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\subfloat{
		{
			\includegraphics[scale=0.7]{figures/left2right/flo_color_juquinha}
		}
		\label{fig:flo_color_juquinha}
	}
	\subfloat{
		{
			\includegraphics[scale=0.7]{figures/left2right/ste_color_juquinha}
		}
		\label{fig:ste_color_juquinha}
	}
    \quad
	\subfloat{
		{
			\includegraphics[scale=0.7]{figures/left2right/bur_color_juquinha}
		}
		\label{fig:bur_color_juquinha}
	}
	\subfloat{
		{
			\includegraphics[scale=0.7]{figures/left2right/sie_color_juquinha}
		}
		\label{fig:sie_color_juquinha}
	}\quad
	\subfloat{
		{
			\includegraphics[scale=0.7]{figures/left2right/stu_color_juquinha}
		}
		\label{fig:stu_color_juquinha}
	}
	\subfloat{
		{
			\includegraphics[scale=0.7]{figures/left2right/jar_color_juquinha}
		}
		\label{fig:jar_color_juquinha}
	}
	\caption{Color Error Diffusion on Cat.}
	\label{fig:color_error_diffusion}
\end{figure}

\begin{figure}[H]
	\centering
	\subfloat{
		{
			\includegraphics[scale=0.7]{figures/left2right/flo_gray_juquinha}
		}
		\label{fig:flo_gray_juquinha}
	}
	\subfloat{
		{
			\includegraphics[scale=0.7]{figures/left2right/ste_gray_juquinha}
		}
		\label{fig:ste_cgray_juquinha}
	}
    \quad
	\subfloat{
		{
			\includegraphics[scale=0.7]{figures/left2right/bur_gray_juquinha}
		}
		\label{fig:bur_gray_juquinha}
	}
	\subfloat{
		{
			\includegraphics[scale=0.7]{figures/left2right/sie_gray_juquinha}
		}
		\label{fig:sie_gray_juquinha}
	}
	\quad
	\subfloat{
		{
			\includegraphics[scale=0.7]{figures/left2right/stu_gray_juquinha}
		}
		\label{fig:stu_gray_juquinha}
	}

	\subfloat{
		{
			\includegraphics[scale=0.7]{figures/left2right/jar_gray_juquinha}
		}
		\label{fig:jar_gray_juquinha}
	}
	\caption{Grayscale error diffusion on Cat.}
	\label{fig:gray_error_diffusion}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\subfloat{
		{
			\includegraphics[scale=0.7]{figures/left2right/flo_color_bee}
		}
		\label{fig:l2r_flo_color_bee}
	}
	\subfloat{
		{
			\includegraphics[scale=0.7]{figures/right2left/flo_color_bee}
		}
		\label{fig:r2l_flo_color_bee}
	}
	\quad
	\subfloat{
		{
			\includegraphics[scale=0.7]{figures/zigzag/flo_color_bee}
		}
		\label{fig:zz_flo_color_bee}
	}
	\caption{Color traversal direction on Girl.}
	\label{fig:color_traversal_l2r}
\end{figure}

\begin{figure}[H]
	\centering
	\subfloat{
		{
			\includegraphics[scale=0.7]{figures/left2right/flo_gray_bee}
		}
		\label{fig:l2r_flo_gray_bee}
	}
	\subfloat{
		{
			\includegraphics[scale=0.7]{figures/right2left/flo_gray_bee}
		}
		\label{fig:r2l_flo_gray_bee}
	}
	\quad
	\subfloat{
		{
			\includegraphics[scale=0.7]{figures/zigzag/flo_gray_bee}
		}
		\label{fig:zz_flo_gray_bee}
	}
	\caption{Grayscale traversal direction on Girl.}
	\label{fig:gray_traversal_l2r}
\end{figure}
